---
title: "AB_Test"
author: "Niki Chen"
date: "6/15/2021"
output: pdf_document
---

```{r}
library(readr)
ab_test <- read_csv("ads_test.csv")
ab_test <- cbind(ab_test,"Test" = ifelse(ab_test$group == "control", "A","B"))
head(ab_test)
```
```{r}
# calculate clk rate
library(plyr)
ddply(ab_test,
      .(Test),
      summarise,
      clr = sum(clk)/length(clk))   
```

### From above, we could find that the clk rate for Test A is 12.05% and the clk rate for Test B is 12.30%.


```{r}
ads_test <- read_csv("ads_test.csv")
ads_test <- ads_test[,c(4,6)]
head(ads_test, 10)
prop <- table(ads_test)
prop
prop_abs <- addmargins(prop)
prop_abs
prop_rel <- prop.table(prop, 1)
prop_rel
prop.test(prop,correct=F,alternative = "greater")
#prop.test(n=c(147239, 147239),x=c(147239*0.1204776, 147239*0.1229701), alternative = "less")
```

### Denotes the click rate for test B (advertising_pid = 430539_1007) is P0 and the click rate for test A (advertising_pid = 430548_1007) is P1

### The hypothesis:  

$H_{0}$ : P0 (The click rate for Test B) <= P1 (The click rate for test A)

$H_{1}$ : P0 (The click rate for Test B) > P1 (The click rate for test A)

### Since P value is 0.0193, which is less than 0.05 ($\alpha$ = 0.05), we reject $H_0$ and conclude that P0 (The click rate for Test B) > P1 (The click rate for test A)

```{r}
ab_test_summary <- ddply (ab_test,
                          .(Test),
                          users=length(user_id),
                          summarise,
                          cl=sum(clk),
                          clr = sum(clk)/length(clk))
                         
head(ab_test_summary)
```

### Conclusion: Accoding to the prop.test and ab_test_summary table, with the same amount users, we could conclude that the effects of test B is better than the effects of test A, and test B (advertising_pid = 430539_1007) has more clicks and higher click rate, which sugests that we should choose test B and increase the advertising of advertising_pid = 430539_1007.




